A holomorphic approach to membranes and fivebranes

### 2022-07-18 fivebranes/intro.tex
updates

\documentclass[11pt]{amsart}
%
%%\usepackage{../macros-master}
\usepackage{macros-fivebrane}
%
\begin{document}

\section{Introduction}

>>>>

%\documentclass[11pt]{amsart}
%
%%\usepackage{../macros-master}
%\usepackage{macros-fivebrane}
%
%\begin{document}

\section{Introduction}
Superconformal field theories admit a plethora of exactly computable, protected quantities, giving them a distinguished role in supersymmetric physics. Since it is believed that all supersymmetric field theories flow to superconformal fixed points, such quantities provide robust invariants of supersymmetric field theories. Examples of such a quantities are superconformal indices, which are generating functions for the R-charges of BPS local operators. Crucial steps towards a more microscopic understanding of superconformal indices were taken in \cite{}, articulated through the construction of twisting.

Introduced by Witten \cite{} and further developed by Costello \cite{}, twisting refers to a fixed-point construction for field theories equipped with the action of a supersymmetry algebra. Operationally, one modifies the BRST differential of the theory by a nilpotent supercharge - the result is a theory on which the translations in the image of the supercharge act homotopically trivially. Every supersymmetric field theory admits a so-called minimal twist; the resulting theory is a holomorphic-topological field theory that is holomorphic in the maximal number of spacetime directions. One of the insights of \cite{} was that superconformal indices counts exactly local operators in the minimal twist.
